Jug: Software for Reproducible Computation

### 2011-11-23 paper.tex
TXT Add example
This is from my own research, so it's a real-life example

\section{Methods}
\section{Example}
\section{Development of Jug}
Jug is available under the MIT software license, which grants the user right to
use, copy, and modify the code almost at will. It is developed using the git
version control tool, with the project being hosted on the github
platform.\footnote{The jug project is available at
\url{https://www.github.com/luispedro/jug}.} An open mailing-list provides
support and reported bugs are generally fixed within hours.

>>>>

\section{Methods}
\section{Example}
I will present an example from my research. Although it introduces some
unnecessary complexity, it has the advantage of being a real-life example of
the usage of jug.

The goal of this project was to demonstrate that using local features, in
particular speeded-up robust features (henceforth,
\textsc{surf})~\cite{surf-paper} improves over image-global features for
classification of microscope images. A variation of standard \textsc{surf},
\textsc{surf}-ref, was introduced and tested.

To evaluate classification, the dataset is broken up into 10~pieces and each of
the pieces is held-out of the analysis and then used to evaluate analysis (the
final result is the average of all ten values). This is known as
cross-validation. In this case, I use another library (which I also wrote)
which has a builtin method for jug-aware cross-validation.

\begin{python}
from jug import TaskGenerator, CachedFunction

# pyslic is used for subcellular location analysis
import pyslic

# milk (machine learning toolkit)
from milk.ext.jugparallel import nfoldcrossvalidation

datasets = [ 'data0', 'data1', ]
featuresets = [ 'field-dna+', 'surf', 'surf-ref', ]

def load(dset):
    '''
    This function assumes that the images are stored in ../data/dset with
    filenames matching the pattern
    label-(protein|dna)-([0-9]).tiff
    '''
    from os import listdir
    images = []
    base = '../data/'+dset
    for path in listdir(base):
        if not 'protein' in path: continue
        label = path.split('-')[0]
        # We only store paths and will load data on demand
        # This save memory.
        im = pyslic.Image({
                'protein': base + path,
                'dna' : base + path.replace('protein','dna')
                })
        im.label = label
        images.append(im)
    return images

# pyslic.computefeatures takes an image and an identifier of the feature set
# and returns a set of features (as a numeric array).
#
# TaskGenerator can be used directly to adapt existing functions
computefeatures = TaskGenerator(pyslic.computefeatures)

# or it can be used as a decorator on a newly defined function
@TaskGenerator
def output(cmatrix, dset, fset):
    output = file('results/cmatrix-'+dset+'-'+fset+'.txt', 'w')
    print >>output, cmatrix
    output.close()

features = []
for dset in datasets:
    images = CachedFunction(load, dset)
    labels = [im.label for im in images]
    for fset in featuresets:
        features = [computefeatures(im, fset) for im in images]
        cmatrix = nfoldcrossvalidation(features, labels)
        output(cmatrix, dset, fset)
\end{python}

\section{Development of Jug}
Jug is available under the MIT software license, which grants the user right to
use, copy, and modify the code almost at will. It is developed using the git
version control tool, with the project being hosted on the github
platform.\footnote{The jug project is available at
\url{https://www.github.com/luispedro/jug}.} An open mailing-list provides
support and reported bugs are generally fixed within hours.
